---
title: "Music Insights Modeling"
author: "Makena Haroldson"
date: "November 19, 2019"
output:
  html_document:
    df_print: paged
---


Uploading Data Cleaning
```{r}
include <- function(library_name){
  if( !(library_name %in% installed.packages()) )
    install.packages(library_name) 
  library(library_name, character.only=TRUE)
}

suppressMessages(include("tidyverse"))
suppressMessages(include("knitr"))
suppressMessages(include("caret")) #predictive models
suppressMessages(purl("Insights.Rmd", output = "part1.r"))
suppressMessages(source("part1.r"))
```

We now can get the average of each persons rating and append it to the person table. Once we do so, we can make a predictions based on a person average rating.
```{r}
#gets the average of person rating
aveRatings <- aggregate(rating ~ pseudonym, preferences, mean)
person_extended <- full_join(aveRatings, person, by = "pseudonym")

#p= 75% split
#dependent variable is 'rating' and you want to see if 'academic_level, sex etc' have any influence on rating
sample_selection <- person_extended$academic_level %>%
            createDataPartition(p = 0.75, list = FALSE)

train <-person_extended[sample_selection, ]
test <-person_extended[-sample_selection,]

#random seed to generate random number
set.seed(54)

#makes model
train_model <- lm(data = person_extended, formula=  rating ~ academic_level + sex + academic_major + year_born, date = train)
summary(train_model)

#p-value: 0.239
predictions <- train_model %>% predict(test)
aveRatings


#r^2 is the correlation, how strong the correlation is (root it, 1 being stronger correlation)
R2 <- R2(predictions, test$rating)
R2

# the smaller the number is, the more accurate the value
MAE <-MAE(predictions, test$rating)
MAE
```

From our p-value (.239), we see that the a person's average rating shows no correlation to any other properties of a person. The p-value is greater than .05, the r^2 value low (better to be closer to 1), and the MAE value is high (better to have a smaller value).


